### 2022-02-15 introduction/introduction.tex
separation?

The initial study of this formalism and the rules to reason about statements in
it was very prolific. In 1930 G\"odel \cite{kg-30-completeness-theorem} showed
that there is a system of inference rules (calculus) such that for any valid
statement a proof of validity can be constructed in this system. Around the same
time, the first computers were leaving the imagination of the engineers and
began to automate many complicated processes.  Naturally, the question as to
whether a computer can decide if a first-order statement is valid (i.e., a
theorem) arose. Church \cite{ac-36-fol-undecidable} and Turing
\cite{tm-37-undecidable} answered this question negatively in 1936.

@@

Proof assistants (or interactive theorem provers) are programs which allow users
to describe a theory formally and to write proofs of the statements about this theory
using inference system rules of the proof assistant. These
programs can then check if the given proof is correct. As their core is usually
small and well-tested, proofs that pass the checking phase are considered
trustworthy.

>>>>

\paragraph{Automatic Theorem Proving}The initial study of this formalism and the rules to reason about statements in
it was very prolific. In 1930 G\"odel \cite{kg-30-completeness-theorem} showed
that there is a system of inference rules (calculus) such that for any valid
statement a proof of validity can be constructed in this system. Around the same
time, the first computers were leaving the imagination of the engineers and
began to automate many complicated processes.  Naturally, the question as to
whether a computer can decide if a first-order statement is valid (i.e., a
theorem) arose. Church \cite{ac-36-fol-undecidable} and Turing
\cite{tm-37-undecidable} answered this question negatively in 1936.

@@

\paragraph{Proof Assistants and Hammers} Proof assistants (or interactive theorem provers) are programs which allow users
to describe a theory formally and to write proofs of the statements about this theory
using inference system rules of the proof assistant. These
programs can then check if the given proof is correct. As their core is usually
small and well-tested, proofs that pass the checking phase are considered
trustworthy.
